Formalizing Stack Safety as a Security Property

### 2022-11-06 submission5/noexceptions.tex
more typos

While this notion of integrity is simple, it is stricter than necessary for many purposes.
For example, it arguably doesn't matter if {\tt f} overwrites {\tt main}'s data provided that {\tt main} never
reads that corrupted data.  This is the justification behind the lazy micro-policy~\cite{??}:
the monitor permits the caller to write into the
callee's frame, but taints that write so that the callee cannot read it later without
triggering a failstop. More generally, the corruption can be considered acceptable
as long as it does not affect {\tt main}'s observable behavior. \apt{Maybe justify this
  point of view by appeal to standard security notions?}
To characterize this situation, we define a state element to be \emph{irrelevant}
if its value can be replaced with any other value without changing the observable behavior
of the machine. More precisely, for a set of elements \(\components\),
a pair of states \(\mach\) and \(\nach\)
are {\em \(\components\)-variants} if t nhey agree on the value of every
element except those in \(\components\), and share the same policy state\apt{hopefully can remove this last}.
The elements of \(\components\) are \emph{irrelevant} in \(\mach\) if every variant state produces an equivalent trace
(see Section \ref{sec:events}); all other elements are \emph{relevant}.
We characterize \emph{observational integrity} as the property that
every \emph{relevant} element that is \(\sealed\) under the callee's view is restored
to its original value at the return point.

@@

The example in Figure \ref{subfig:integrity} modifies the value of {\tt sensitive},
which is \(\sealed\). Figure \ref{fig:variant} shows the state just after the all at step 5,
assuming that {\tt sec} is 5. Similar to WBCF, we will define
\(int\) \apt{suggest $Int$} as a predicate on states that holds if
all relevant sealed addresses in \(s\) are the same as after step 5.
We once again require that \(int\) hold on the state following the matching return.
That state is reached by step 9. Although {\tt sensitive} has changed, it might be
irrelevant. Consider a variant state in which {\tt sensitive} has any other value, arbitrarily
choosing 43. As execution continues after the return from the original state, it
passes the {\tt if}-test on {\tt sensitive}, whereas the execution from the variant does not, resulting
in differing outputs. Therefore {\tt sensitive} is relevant, so \(int\) does not hold,
and integrity has indeed been violated.

>>>>

While this notion of integrity is simple, it is stricter than necessary for many purposes.
For example, it arguably doesn't matter if {\tt f} overwrites {\tt main}'s data provided that {\tt main} never
reads that corrupted data.  This is the justification behind the lazy micro-policy~\cite{??}:
the monitor permits the caller to write into the
callee's frame, but taints that write so that the callee cannot read it later without
triggering a failstop. More generally, corruption by {\tt f} can be considered acceptable
as long as it does not affect {\tt main}'s observable behavior. \apt{Maybe justify this
  point of view by appeal to standard security notions?}
To characterize this situation, we define a state element to be \emph{irrelevant}
if its value can be replaced with any other value without changing the observable behavior
of the machine. More precisely, for a set of elements \(\components\),
a pair of states \(\mach\) and \(\nach\)
are {\em \(\components\)-variants} if they agree on the value of every
element except those in \(\components\), and share the same policy state\apt{hopefully can remove this last}.
The elements of \(\components\) are \emph{irrelevant} in \(\mach\) if every variant state produces an equivalent trace
(see Section \ref{sec:events}); all other elements are \emph{relevant}.
We characterize \emph{observational integrity} as the property that
every relevant element that is \(\sealed\) under the callee's view is restored
to its original value at the return point.

@@

The example in Figure \ref{subfig:integrity} modifies the value of {\tt sensitive},
which is \(\sealed\). Figure \ref{fig:variant} shows the state just after the call at step 5,
assuming that {\tt sec} is 5. Similar to WBCF, we will define
\(int\) \apt{suggest $Int$} as a predicate on states that holds if
all relevant sealed addresses in \(s\) are the same as after step 5.
We once again require that \(int\) hold on the state following the matching return.
That state is reached by step 9. Although {\tt sensitive} has changed, it might be
irrelevant. Consider a variant state in which {\tt sensitive} has any other value, arbitrarily
choosing 43. As execution continues after the return from the original state, it
passes the {\tt if}-test on {\tt sensitive}, whereas the execution from the variant does not, resulting
in differing outputs. Therefore {\tt sensitive} is relevant, so \(int\) does not hold,
and integrity has indeed been violated.
